Left-linear rewriting in adhesive categories

### 2024-04-23 concur/fusione.tex
typo

Left-linear rewriting systems on $\cat{EGraphs}$,\todo{A: sostituirei ``, i.e. in which'' con ``where''. Giusto?} i.e.~in which the right half of a rule is mono but not regular in general, 
are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one at the receiver,
but put instead in the same equivalence class, thus better tracing the causal dependencies among processes reductions.
\end{example}

>>>>

Left-linear rewriting systems on $\cat{EGraphs}$, %\todo{A: sostituirei ``, i.e. in which'' con ``where''. Giusto?} 
i.e.~where the right half of a rule is mono but not regular in general, 
are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one at the receiver,
but put instead in the same equivalence class, thus better tracing the causal dependencies among processes reductions.
\end{example}
